---
title: "Algorithmic Advice Study Analysis"
output: html_document
---

Import libraries
```{r}
library(tidyverse)
```

Load data

```{r}
data <- read_csv("data/first340_data.csv") 
```

Calculate the number & percent of people who selected each advice type

```{r}
count_adviceTypes <- data %>%
  filter(!is.na(adviceType) & attentionQ==20) %>% # removing ppl who failed attention check + NA in advice type
  group_by(adviceType) %>%
  count(adviceType) %>% 
  ungroup() %>% 
  mutate(percent_total = n/sum(n))
     
count_adviceTypes       
```

```{r}
ggplot(data=count_adviceTypes,aes(x=adviceType,y=percent_total))+geom_point()+ylim(0,1)
```

Marascuillo procedure for comparing multiple proportions

```{r}
#chi-sq = 7.815
sqrt_chi <- sqrt(7.815)

k <- length(unique(count_adviceTypes$adviceType))
n_comparisons <- k*(k-1)/2

M_procedure <- list("label"=character(),"difference"=numeric(),"r"=numeric())

for(i in 1:n_comparisons){
  for(j in 2:n_comparisons-1){
    if(i+j<=k){
      i_th_lbl <- count_adviceTypes$adviceType[i]
      j_th_lbl <- count_adviceTypes$adviceType[i+j]
      
      i_th <- count_adviceTypes$percent_total[i]
      j_th <- count_adviceTypes$percent_total[i+j]
      
      I_th = i_th*(1-i_th)/count_adviceTypes$n[i]
      J_th = j_th*(1-j_th)/count_adviceTypes$n[i+j]
      r_ij = sqrt_chi*sqrt(I_th + J_th) 
      
      M_procedure$label <- c(M_procedure$label,paste0(i_th_lbl,"-",j_th_lbl))
      M_procedure$difference <- c(M_procedure$difference,abs(i_th - j_th))
      M_procedure$r <- c(M_procedure$r,r_ij)
    }
  }
}

M_procedure <- as.data.frame(cbind(M_procedure$label,M_procedure$difference,M_procedure$r))
colnames(M_procedure) <- c("label","difference","r")

M_procedure$difference <- as.numeric(as.character(M_procedure$difference))
M_procedure$r <- as.numeric(as.character(M_procedure$r))
```

```{r}
str(M_procedure)
```


```{r}
# Marascuillo procedure for comparing multiple proportions
for(i in 1:nrow(M_procedure)){
  if(M_procedure$difference[i] > M_procedure$r[i]){
    M_procedure$significant[i] <- 1
    }else{
      M_procedure$significant[i] <- 0
    }
  }
M_procedure
```

Check how many people exposed to each condition

```{r}
xtab <- data %>%
  filter(!is.na(adviceType) & attentionQ==20) %>%
  group_by(optionB) %>% 
  summarize(n=n())
xtab
```

```{r}
xtabs_type_option <- data %>%
  filter(!is.na(adviceType) & attentionQ==20) %>%
  group_by(adviceType,optionB) %>% 
  summarize(n=n()) %>% 
  mutate(optionB = paste0('option_',optionB)) %>% 
  spread('optionB','n')

xtabs_type_option

# option_1 = lower overall infection rate than 'strict' advice
# option_2 = equal overall infection rate than 'strict' advice
# option_3 = higher overall infection rate than 'strict' advice
```

Chi-square analysis 

```{r}
indep_analysis <- xtabs_type_option %>% 
  filter(!is.na(option_1)) %>% 
  column_to_rownames(var="adviceType")

chisq <- chisq.test(indep_analysis)
chisq
```

Print out expected matrix 

```{r}
chisq$expected
```

Extract Pearson residuals to see which cells contribute the most to the chi-square score

```{r}
round(chisq$residuals, 3)
```

```{r}
library(corrplot)
corrplot(chisq$residuals,is.cor=FALSE)
```

- Strong positive correlation between option 3 and strict advice
- Negative correlation between option 3 and relaxed/both advice
- Strong negative correlation between option 1 and strict advice



Contibution in percentage (%)

```{r}
contrib <- 100*chisq$residuals^2/chisq$statistic
round(contrib, 3)
```

Visualize the contribution

```{r}
corrplot(contrib, is.cor = FALSE)
```

- Option 3 is strongly associated with strict advice
